toyData

### 2017-11-08 latex/dataMaid_toyData.Rmd
First round of tests

---
dataMaid: yes
title: toyData
subtitle: "Autogenerated data summary from dataMaid"
date: 2017-10-31 15:34:55
output: pdf_document
documentclass: report
header-includes:
  - \renewcommand{\chaptername}{Part}
  - \newcommand{\fullline}{\noindent\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}}
---
```{r , echo=FALSE, include=FALSE, warning=FALSE, message=FALSE, error=FALSE}
library(ggplot2)
library(pander)
```
# Data report overview
The dataset examined has the following dimensions:

@@

----------------------------------------------------------------------------------
&nbsp;   Variable class     # unique values   Missing observations  Any problems? 
-------- ---------------- ----------------- ---------------------- ---------------
[var1]   factor                           3                13.33 %    $\times$

[var2]   numeric                          7                26.67 %    $\times$

[var3]   factor                           7                 0.00 %    $\times$

[var4]   numeric                         15                 0.00 %    $\times$

[var5]   factor                          15                 0.00 %    $\times$

[var6]   factor                           1                 0.00 %    $\times$    
----------------------------------------------------------------------------------

# Variable list
## var1

@@

## var2

@@

## var3

@@

## var4

@@

## var5

@@

## var6

@@

 *  Report creation time: Tue Oct 31 2017 15:34:55

 *  dataMaid v0.9.7.9000 [Pkg: 2017-10-31 from local (ekstroem/dataMaid@NA)]

>>>>

---
dataMaid: yes
title: toyData
subtitle: "Autogenerated data summary from dataMaid"
date: 2017-11-08 12:08:33
output: pdf_document
documentclass: report
header-includes:
  - \renewcommand{\chaptername}{Part}
  - \newcommand{\fullline}{\noindent\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}}
---
```{r , echo=FALSE, include=FALSE, warning=FALSE, message=FALSE, error=FALSE}
library(ggplot2)
library(pander)
```
# Data report overview
The dataset examined has the following dimensions:

@@

-----------------------------------------------------------------------------------------
&nbsp;          Variable class     # unique values   Missing observations  Any problems? 
--------------- ---------------- ----------------- ---------------------- ---------------
[pill]          factor                           3                13.33 %    $\times$

[events]        numeric                          7                26.67 %    $\times$

[region]        factor                           7                 0.00 %    $\times$

[change]        numeric                         15                 0.00 %    $\times$

[id]            factor                          15                 0.00 %    $\times$

[spotifysong]   factor                           1                 0.00 %    $\times$    
-----------------------------------------------------------------------------------------

# Variable list
## pill

@@

## events

@@

## region

@@

## change

@@

## id

@@

## spotifysong

@@

 *  Report creation time: Wed Nov 08 2017 12:08:33

 *  dataMaid v0.9.7.9000 [Pkg: 2017-11-08 from local (ekstroem/dataMaid@NA)]
